How young children integrate information during word learning

### 2020-05-18 paper/supplementary_material.Rmd
update color scheme

ggplot(item_comp_int, aes(x = value, fill = model, col = model))+
  geom_density(alpha = 0.8, adjust = 2)+
  xlab("value")+
  facet_wrap( ~ item, nrow = 2, scales = 'free')+
  theme_few()+
  xlim(-10,5)+
  theme(legend.position = "bottom")+
  scale_fill_ptol(name = "Model")+
  scale_color_ptol(name = "Model")
```

@@

ggplot(item_comp_slope, aes(x = value, fill = model, col = model))+
  geom_density(alpha = 0.8, adjust = 2)+
  xlab("value")+
  facet_wrap( ~ item, nrow = 2, scales = 'free_y')+
  xlim(-1,4)+
  theme_few()+
  theme(legend.position = "bottom")+
  scale_fill_ptol(name = "Model")+
  scale_color_ptol(name = "Model")
```

@@

ggplot(global_comp, aes(x = value, fill = model, col = model))+
  geom_density(alpha = 0.8, adjust = 2)+
  xlab("value")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()+
  theme(legend.position = "right")+
  scale_fill_ptol(name = "Model")+
  scale_color_ptol(name = "Model")
```

>>>>

ggplot(item_comp_int, aes(x = value, fill = model, col = model))+
  geom_density(alpha = 0.8, adjust = 2)+
  xlab("value")+
  facet_wrap( ~ item, nrow = 2, scales = 'free')+
  theme_few()+
  xlim(-10,5)+
  theme(legend.position = "bottom")+
  scale_fill_colorblind(name = "Model")+
  scale_color_colorblind(name = "Model")
```

@@

ggplot(item_comp_slope, aes(x = value, fill = model, col = model))+
  geom_density(alpha = 0.8, adjust = 2)+
  xlab("value")+
  facet_wrap( ~ item, nrow = 2, scales = 'free_y')+
  xlim(-1,4)+
  theme_few()+
  theme(legend.position = "bottom")+
  scale_fill_colorblind(name = "Model")+
  scale_color_colorblind(name = "Model")
```

@@

ggplot(global_comp, aes(x = value, fill = model, col = model))+
  geom_density(alpha = 0.8, adjust = 2)+
  xlab("value")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()+
  theme(legend.position = "right")+
  scale_fill_colorblind(name = "Model")+
  scale_color_colorblind(name = "Model")
```
